Object Naming in Language and Vision: A Survey and a New Dataset

### 2020-03-12 papers/LREC2020/analysis.tex

As shown in Table~\ref{tab:compare} above, ManyNames gathers many more names per object than previous datasets: 35.3 on average, compared to 1-7.
It also contains the most variability, since objects have on average 5.7 names (compared to 1-1.9).
Figure~\ref{fig:ex-high-low-agreement} shows some example datapoints of ManyNames with high and low name agreement.
ManyNames 
%in in principle suitable to study 
shows high potential use for studying the degree of inter-subject naming agreement, and what factors influence variation.
Data analysis shows that object identification remains an issue in our data, though: Despite our care in filtering out objects that are occluded or have unclear bounding boxes (see\ Section~\ref{sec:data}), we still find many examples where annotators identified different objects for the same bounding box. 
Typically, workers named an adjacent object or one supported by the target object (such as \word{toy/book} instead of \word{bed} in Fig.~\ref{fig:ex-high-low-agreement}, image K), or a part of the target object.
While some of these cases are arguably annotation errors, in many cases it is not possible to distinguish which object is being indicated by the bounding box, as in the \word{bed/sleeping bag} case in Fig.~\ref{fig:ex-high-low-agreement} (image L).
Referential uncertainty of this kind is a roadblock for the use of L\&V resources to study naming variation.
Note that pointing gestures in natural communication are as referentially uncertain as bounding boxes, if not more; however, typically those gestures are grounded in a specific discourse context, which helps to reduce uncertainty.
In future work, we plan to filter out these cases.

\subsection{Naming variation and agreement}
\label{subsec:counts}

We analyze the response sets obtained per object, that is, the set of names and their frequency (number of annotators entering a particular name).
Our analysis of naming variation shows that, on the one hand, we have a fair bit of consistency in the names chosen for objects, and, on the other, also consistent variation.
Figure \ref{fig:ntypes} shows the cumulative histograms for type counts, i.e.\ how many objects have at least $n$\ names, with different frequency thresholds~$t$.
Without any frequency thresholding~\mbox{$t$=1}, that is, allowing names entered by only one annotator, the proportion of instances that have a single name annotated is very small, below\ $10\%$, and there is a long tail of datapoints with many names, up to 19. 
With a reasonable (based on data inspection; names entered by one annotator only have the most noise, which is to be expected) threshold of $t$=2, a bit over $20\%$\ of the objects have one name, almost $50\%$\ up to $3$\ names, and $100\%$\ up to $8$\ names.
This threshold is the one illustrated in Fig.~\ref{fig:ex-high-low-agreement}, which includes names that have at least frequency 2.
The average number of names with this threshold is\ $2.9$, and the most frequent name accounts on average for $75\%$\ of the responses for a given object (Table~\ref{tab:agree}, and see below).
Thus, in our data objects tend to have a preferred name, as expected from work in Psychology \cite{rosch1976basic,jolicoeur1984pictures}, and at the same time there is variation.

\begin{table}
\centering
\small
\begin{tabular}{lccccc}
  \toprule
% & \multicolumn{5}{c}{Instance-level agreement} \\
  domain &    N &         \%top (std) &          H (std) & t=VG &   \%VG \\
  \midrule
  all &  2.9 &  75.2 (21.9) &  0.9 (0.7) &   72.8 &  62.8 \\
  \midrule
  people &  4.3 &  59.0 (20.4) &  1.5 (0.7) &   49.8 &  36.3 \\
  clothing &  3.2 &  70.1 (18.5) &  1.1 (0.6) &   70.2 &  57.4\\
  home &  3.1 &  72.6 (20.7) &  1.0 (0.7) &   78.5 &  64.1 \\
  buildings &  3.0 &  74.7 (20.7) &  1.0 (0.7) &   72.6 &  61.6\\
  food &  2.9 &  76.4 (20.7) &  0.9 (0.7) &   62.9 &  55.2 \\
  vehicles &  2.4 &  76.6 (19.8) &  0.8 (0.6) &   71.1 &  63.9 \\
  animal\_plants &  1.5 &  94.5 (12.1) &  0.2 (0.4) &   93.8 &  91.0\\
\bottomrule
\end{tabular}
\vspace{-0.3cm}
\caption{Agreement in object naming, with a frequency threshold of 2.}
% Domain `an\_pl' is animal\_plants.}
\label{tab:agree}
\end{table}

To further assess agreement on the object names, we check the following measures, computed with $t=2$, with results in Table~\ref{tab:agree}:
\begin{itemize}
\item \textbf{N}: the average number of types in the response set of ManyNames.
\item \textbf{\% top}: the average relative frequency of the most frequent response (shown in percent).
\item \textbf{$H$}: the $H$ agreement measure from \cite{snodgrass}, where 0 is perfect agreement: \mbox{$H = \sum_{i=1}^k p_i~log_2\frac{1}{p_i}$}, 
where $k$\ denotes the number of name types and $p_i$\ is the proportion of name type\ $i$ in the responses. 
\item \textbf{t=VG}: the percentage of items where the top response in ManyNames is the \vg name.
\item \textbf{\% VG}: the average relative frequency of the \vg name in the response set.
\end{itemize}

Apart from the trends mentioned above, it is remarkable that only in 73\% of the cases the most frequent response coincides with the \vg name, and the \vg name accounts for 63\% of the responses on average.
Our dataset can be expected to yield a more robust estimate for so-called entry-point names \cite{jolicoeur1984pictures}, that is, the name that most naturally comes to mind for a given object.
The $H$ measures indicate a fair amount of agreement, a bit lower than in picture norming studies on artificial idealized images (e.g.\ \newcite{snodgrass} report an average $H$ of\ $0.55$), which can be expected when using real images.

If we check agreement by domain, two domains stand out: the \domain{animals\_plants} domain, which is often discussed in the literature and where we find almost perfect agreement\ (\mbox{$H=0.2$}), and the \domain{people} domain with a particularly low agreement.
Across domains, however, we find a large standard deviation for both \%top and $H$, of around\ $20\%$ for all domains except \domain{people}.
This indicates that agreement varies quite a bit across instances, with factors that cannot be attributed to domain only.
The qualitative examples in Figure \ref{fig:ex-high-low-agreement} illustrate this, showing visual instances with very high or low agreement.
These suggest that instances which are more prototypical of a category trigger higher agreement, although further research is necessary to examine the relevant factors.
The following section will examine other sources of variation in object naming.

@@

\subsection{Sources of variation}
\label{subsec:sources}

Previous work on object naming has assumed that variation is mostly along a taxonomic axis, and in particular hierarchical (see Section~\ref{sec:rel-work}).
This parameter does not seem to explain the variation in ManyNames. 
Table \ref{tab:rel} shows the distribution of the lexical relations between ManyNames responses and the original \vg annotation, estimated from WordNet.
To obtain these data, we exploited the synset annotation in the \vg names, and added automatic linking for the additional ManyNames names, with a simple first-sense heuristic.%
\footnote{To detect hypernyms, we use the hypernym closure of the synset with a depth of 10; the other relations are straightforward. The coverage of WordNet for our name data is satisfactory (90\%\ of the name types, accounting for 97\%\ of the tokens).}
As shown in the table, in the vast majority of cases, no hierarchical relation between the name and the synset can be retrieved from WordNet.
Even factoring in the noise introduced by referential uncertainty, it is clear that a good portion of our data cannot be explained by variation in the level of abstraction of the chosen name. 
Among the names that do have a taxonomic relation to the synset, hypernyms are the most frequent, meaning that our annotators often went for a more general name than the \vg annotators.
%%In this section, we take a closer look at the lexical variation we observe in our data set. 
%We analyze the data points where participants attributed different names to the same object and extract a set of  pairwise \textbf{naming variants}. These naming variants correspond to pairs of words that can be used interchangeably to name certain objects.
%For each object, we extract the set of naming variants $s = \{ (w_{top},w_2), (w_{top},w_3), (w_{top},w_4),... \}$  where $w_{top}$ is the most frequent name annotated for the object and $w_2 ... w_n$ constitute the less frequent alternatives of $w_{top}$.  The  \textbf{type frequency} of a naming variant $(w_{top},w_x)$ corresponds to the number of objects where this variant occurs. The \textbf{token frequency} of $(w_{top},w_x)$ corresponds the count of all annotations where $w_x$ has been used instead of $w_{top}$.
%In Table \ref{tab:exvariants}, we show the naming variants with the highest raw token frequency for each domain. 
%The naming variants can be grouped according to their lexical relation, as follows:
%
%\begin{itemize}
%\item \textbf{synonymy}: e.g.\ aircraft vs. airplane 
%\item \textbf{hyponymy}: e.g.\ man vs. person
%\item \textbf{co-hyponymy}: e.g.\ swan vs. goose
%\item \textbf{no relation}: e.g.\  desk vs. apple
%\end{itemize}
%\cs{Shouldn't we mention that we consider only simple move-up hypernymy relations?}

@@

In a qualitative analysis, we found the following types of variation in the data, illustrated with examples in Figure~\ref{fig:ex-high-low-agreement}.
\textbf{Cross-classification}: a substantial group are names conceptualizing alternative aspects of the same object (e.g. \textit{toast/dessert}, image C).
\textbf{Conceptual disagreement}: as we did not filter objects for prototypicality, our data mirrors a certain amount of disagreement between speakers as to what an object is (\textit{bed/bench}, images J).
\textbf{Metonymy}: we find examples reminiscent of metonymy discussed in the linguistic literature \cite{pustejovsky1991generative} where logically related parts of an object stand in as its name (\textit{burger/basket}, image B). 
\textbf{Issues with WordNet}: due to WordNet's fine-grained hierarchy, it is difficult to retrieve certain loose synonyms or hypernyms (\textit{robe/dress}, image not shown).
%As it is non-trivial to separate these phenomena, we leave a quantitative analysis for future work.
%
\begin{table}[t]
%\small
\centering
\setlength{\tabcolsep}{2pt}
\begin{tabular}{lcc|p{2.5cm}}
\toprule
         relation & \% types & \% tokens & \it ex: jacket \\
\midrule
% meronym &  0.1 &  0.2 \\
% holonym &  0.1 &  0.4 \\
 word-not-covered &  10.6 &  2.6 & \it outdoor vest\\
\midrule
 synonym &  1.1 &  1.1 & \it hoodie  \\
 hyponym &  2.2 &  3.8 & \it parka\\ %, blazer \\
 co-hyponym &  3.1 &  5.9 & \it raincoat\\
 hypernym &  10.5 &  27.7 & \it clothing \\%, coat\\
 rel-not-covered &  72.2 &  58.3 & \it sweatshirt\\%, man\\
\bottomrule
\end{tabular}
\caption{Lexical relations of naming variants in ManyNames to annotated \vg synset, averaged over synsets, with examples of variants for \word{jacket}.}
\label{tab:rel}
\vspace{-0.5cm}
\end{table}

\iffalse
*********
Existing large-scale collections of labels or names of objects in L\&V provide simple annotations of individual objects with canonicalized name sets.
When humans agree only around 70\% of the cases in how to name an object, it is not clear that the data can be taken as a gold standard in multi-label classification setting, as is commonly done in Computer Vision.
% At the same time, compared to annotation and modeling frameworks in Computer Vision that frame the problem as an object labeling task, our data shows a much lower agreement than what should be expected if object names were indeed entirely canonical,
See e.g.\ the ResNet which achieves a top-1 error rate of 25\% on ILSVRC 2015. \gbt{It is not clear to me what this means: what kind of data is this? how does this result relate to our point? -- @Carina, expand?}
\fi

>>>>

As shown in Table~\ref{tab:compare} above, ManyNames gathers many more names per object than previous datasets: $35.3$~on average, compared to~$1-7$.
It also contains the most variability, since objects have on average $5.7$~names (compared to~\mbox{$1-1.9$}).
Figure~\ref{fig:ex-high-low-agreement} shows some example datapoints of ManyNames with high and low name agreement.
ManyNames 
%in in principle suitable to study 
shows high potential use for studying the degree of inter-subject naming agreement, and what factors influence variation.
Data analysis shows that object identification remains an issue in our data, though: Despite our care in filtering out objects that are occluded or have unclear bounding boxes (see\ Section~\ref{sec:data}), we still find many examples where annotators identified different objects for the same box. 
Typically, workers named an adjacent object or one supported by the target object (such as \word{toy/book} instead of \word{bed} in Fig.~\ref{fig:ex-high-low-agreement}, image K), or a part of the target object.
While some of these cases are arguably annotation errors, in many cases it is not possible to distinguish which object is being indicated by the  box, as in the \word{bed/sleeping bag} case in Fig.~\ref{fig:ex-high-low-agreement} (image L).
Referential uncertainty of this kind is a roadblock for the use of L\&V resources to study naming variation.
Note that pointing gestures in natural communication are as referentially uncertain as bounding boxes, if not more; however, typically those gestures are grounded in a specific discourse context, which helps to reduce uncertainty.
In future work, we plan to filter out these cases.

\subsection{Naming Variation and Agreement}
\label{subsec:counts}

We analyze the response sets obtained per object, that is, the set of names and their frequency (number of annotators entering a particular name).
Our analysis of naming variation shows that, on the one hand, we have a fair bit of consistency in the names chosen for objects, and, on the other, also consistent variation.
Figure \ref{fig:ntypes} shows the cumulative histograms for type counts, i.e.\ how many objects have at least $n$\ names, with different frequency thresholds~$t$.
Without any frequency thresholding~\mbox{$t$=1}, that is, allowing names entered by only one annotator, the proportion of instances that have a single name annotated is very small, below\ $10\%$, and there is a long tail of datapoints with many names, up to 19. 
With a reasonable (based on data inspection; names entered by one annotator only have the most noise, which is to be expected) threshold of $t$=2, a bit over $20\%$\ of the objects have one name, almost $50\%$\ up to $3$\ names, and $100\%$\ up to $8$\ names.
This threshold is the one illustrated in Fig.~\ref{fig:ex-high-low-agreement}, which shows names that have at least frequency 2.
The average number of names with this threshold is\ $2.9$, and the most frequent name accounts on average for $75\%$\ of the responses for a given object (Table~\ref{tab:agree}, and see below).
Hence, in our data, objects tend to have a preferred name, as expected from work in Psychology \cite{rosch1976basic,jolicoeur1984pictures}, but at the same time there is variation.

\begin{table}
\centering
\small
\begin{tabular}{lccccc}
  \toprule
% & \multicolumn{5}{c}{Instance-level agreement} \\
  Domain &    N &         \%top (std) &          H (std) & t=VG &   \%VG \\
  \midrule
  all &  2.9 &  75.2 (21.9) &  0.9 (0.7) &   72.8 &  62.8 \\
  \midrule
  people &  4.3 &  59.0 (20.4) &  1.5 (0.7) &   49.8 &  36.3 \\
  clothing &  3.2 &  70.1 (18.5) &  1.1 (0.6) &   70.2 &  57.4\\
  home &  3.1 &  72.6 (20.7) &  1.0 (0.7) &   78.5 &  64.1 \\
  buildings &  3.0 &  74.7 (20.7) &  1.0 (0.7) &   72.6 &  61.6\\
  food &  2.9 &  76.4 (20.7) &  0.9 (0.7) &   62.9 &  55.2 \\
  vehicles &  2.4 &  76.6 (19.8) &  0.8 (0.6) &   71.1 &  63.9 \\
  animal\_plants &  1.5 &  94.5 (12.1) &  0.2 (0.4) &   93.8 &  91.0\\
\bottomrule
\end{tabular}
\vspace{-0.3cm}
\caption{Agreement in object naming, with a frequency threshold of~$2$.}
% Domain `an\_pl' is animal\_plants.}
\label{tab:agree}
\end{table}

To further assess agreement on the object names, we check the following measures, computed with \mbox{$t$=$2$}, with results in Table~\ref{tab:agree}:
\begin{itemize}
\item \textbf{N}: the average number of types in the response set. %of ManyNames.
\item \textbf{\% top}: the average relative frequency of the most frequent response (shown in percent).
\item $\mathbf{H}$: the $H$ agreement measure from \cite{snodgrass}, where $0$~is perfect agreement: \mbox{$H = \sum_{i=1}^k p_i~log_2\frac{1}{p_i}$}, 
where $k$~denotes the number of name types and $p_i$~is the proportion of type~$i$ in the responses. 
\item \textbf{t=VG}: the percentage of items where the top response in ManyNames is the \vg name.
\item \textbf{\% VG}: the average relative frequency of the \vg name in the response set.
\end{itemize}

Apart from the trends mentioned above, it is remarkable that only in $73$\%~of the cases the most frequent response coincides with the \vg name, and the \vg name accounts for $63$\%~of the responses on average.
Our dataset can be expected to yield a more robust estimate for so-called entry-point names \cite{jolicoeur1984pictures}, that is, the name that most naturally comes to mind for a given object.
The $H$ measures indicate a fair amount of agreement, a bit lower than in picture norming studies on artificial idealized images (e.g.\ \newcite{snodgrass} report an average $H$ of~$0.55$), which can be expected when using real images.

If we check agreement by domain, two domains stand out: the \domain{animals\_plants} domain, which is often discussed in the literature and where we find almost perfect agreement\ (\mbox{$H=0.2$}), and the \domain{people} domain with a particularly low agreement.
Across domains, however, we find a large standard deviation for both \%top and $H$, of around\ $20\%$ for all domains except \domain{people}.
This indicates that agreement varies quite a bit across instances, with factors that cannot be attributed to domain only.
The qualitative examples in Figure \ref{fig:ex-high-low-agreement} illustrate this, showing instances with very high or low agreement.
These suggest that instances which are more prototypical of a category trigger higher agreement, although further research is necessary to examine the relevant factors.
The following section will examine other sources of variation in object naming.

@@

\subsection{Sources of Variation}
\label{subsec:sources}

Previous work on object naming has assumed that variation is mostly along a taxonomic axis, and in particular hierarchical (see Section~\ref{sec:rel-work}).
This parameter does not seem to explain the variation in ManyNames. 
Table \ref{tab:rel} shows the distribution of the lexical relations between ManyNames responses and the original \vg annotation, estimated from WordNet.
To obtain these data, we exploited the synset annotation in the \vg names, and added automatic linking for the additional ManyNames names, with a simple first-sense heuristic.%
\footnote{To detect hypernyms, we use the hypernym closure of the synset with a depth of $10$; the other relations are straightforward. The coverage of WordNet for our name data is satisfactory ($90$\%\ of the name types, accounting for $97$\%\ of the tokens).}
As shown in the table, in the vast majority of cases, no hierarchical relation between the name and the synset can be retrieved from WordNet.
Even factoring in the noise introduced by referential uncertainty, it is clear that a good portion of our data cannot be explained by variation in the level of abstraction of the chosen name. 
Among the names that do have a taxonomic relation to the synset, hypernyms are the most frequent, meaning that our annotators often went for a more general name than the \vg annotators.
%%In this section, we take a closer look at the lexical variation we observe in our data set. 
%We analyze the data points where participants attributed different names to the same object and extract a set of  pairwise \textbf{naming variants}. These naming variants correspond to pairs of words that can be used interchangeably to name certain objects.
%For each object, we extract the set of naming variants $s = \{ (w_{top},w_2), (w_{top},w_3), (w_{top},w_4),... \}$  where $w_{top}$ is the most frequent name annotated for the object and $w_2 ... w_n$ constitute the less frequent alternatives of $w_{top}$.  The  \textbf{type frequency} of a naming variant $(w_{top},w_x)$ corresponds to the number of objects where this variant occurs. The \textbf{token frequency} of $(w_{top},w_x)$ corresponds the count of all annotations where $w_x$ has been used instead of $w_{top}$.
%In Table \ref{tab:exvariants}, we show the naming variants with the highest raw token frequency for each domain. 
%The naming variants can be grouped according to their lexical relation, as follows:
%
%\begin{itemize}
%\item \textbf{synonymy}: e.g.\ aircraft vs. airplane 
%\item \textbf{hyponymy}: e.g.\ man vs. person
%\item \textbf{co-hyponymy}: e.g.\ swan vs. goose
%\item \textbf{no relation}: e.g.\  desk vs. apple
%\end{itemize}
%\cs{Shouldn't we mention that we consider only simple move-up hypernymy relations?}

@@

In a qualitative analysis, we found the following types of variation in the data, illustrated with examples in Figure~\ref{fig:ex-high-low-agreement}.
\textbf{Cross-classification}: a substantial group are names conceptualizing alternative aspects of the same object (e.g. \word{toast/dessert}, image C).
\textbf{Conceptual disagreement}: as we did not filter objects for prototypicality, our data mirrors a certain amount of disagreement between speakers as to what an object is (\word{bed/bench}, images J).
\textbf{Metonymy}: we find examples reminiscent of metonymy discussed in the linguistic literature \cite{pustejovsky1991generative} where logically related parts of an object stand in as its name (\word{burger/basket}, image B). 
\textbf{Issues with WordNet}: due to WordNet's fine-grained hierarchy, it is difficult to retrieve certain loose synonyms or hypernyms (\word{robe/dress}, image not shown).
%As it is non-trivial to separate these phenomena, we leave a quantitative analysis for future work.
%
\cs{TO ADD: What does ManyNames provide, that WordNet can't: out-of-vocabulary words; we observe instance-based variation, WordNet is class-based: valid (co-)hyponyms, different most preferred name depending on instance, variations which are not due to taxonomic relations}
\begin{table}[t]
%\small
\centering
\setlength{\tabcolsep}{2pt}
\begin{tabular}{lcc|p{2.5cm}}
\toprule
         relation & \% types & \% tokens & \it ex: jacket \\
\midrule
% meronym &  0.1 &  0.2 \\
% holonym &  0.1 &  0.4 \\
 word-not-covered &  10.6 &  2.6 & \it outdoor vest\\
\midrule
 synonym &  1.1 &  1.1 & \it hoodie  \\
 hyponym &  2.2 &  3.8 & \it parka\\ %, blazer \\
 co-hyponym &  3.1 &  5.9 & \it raincoat\\
 hypernym &  10.5 &  27.7 & \it clothing \\%, coat\\
 rel-not-covered &  72.2 &  58.3 & \it sweatshirt\\%, man\\
\bottomrule
\end{tabular}
\caption{Lexical relations of naming variants in ManyNames to annotated \vg synset, averaged over synsets, with examples of variants for \word{jacket}.}
\label{tab:rel}
\vspace{-0.5cm}
\end{table}

\iffalse
*********
Existing large-scale collections of labels or names of objects in L\&V provide simple annotations of individual objects with canonicalized name sets.
When humans agree only around 70\% of the cases in how to name an object, it is not clear that the data can be taken as a gold standard in multi-label classification setting, as is commonly done in Computer Vision.
% At the same time, compared to annotation and modeling frameworks in Computer Vision that frame the problem as an object labeling task, our data shows a much lower agreement than what should be expected if object names were indeed entirely canonical,
See e.g.\ the ResNet which achieves a top-1 error rate of $25$\% on ILSVRC 2015. \gbt{It is not clear to me what this means: what kind of data is this? how does this result relate to our point? -- @Carina, expand?}
\fi

### 2020-03-12 papers/LREC2020/intro.tex

% GBT revision (I've re-organized the material into paragraphs differently and gone more directly to object names):
A central issue in Language \& Vision (L\&V) is how speakers refer to objects. 
This is most prominent for referring expression generation and interpretation~\cite{Kazemzadeh2014,mao15,Yu2016}, but it also pervades virtually any other L\&V task, such as caption generation or visual dialogue \cite{fangetal:2015,devlin:imcaqui,das2017visual,vries2017guesswhat}.
One of the central components of referring expressions are \textit{object names}; for instance, speakers may name the left object in Figure \ref{fig:cake} `cake', `food', or `dessert', a.o.
This aspect of reference has been understudied in Computational Linguistics and L\&V; as a consequence, it is not clear to what extent current L\&V models capture human naming behavior.
% the factors affecting the choice of a name are far from clear, as is the potential of current L\&V models to successfully model naming data.

@@

% SUBMITTED VERSION:
% Compared to experimental work on perception and language grounding, however, recent data collections in L\&V capture a rather limited amount of inter-speaker variation.
% For instance, picture naming norms used in Psycholinguistics record naming responses for hundreds of speakers for the same object  \cite{snodgrass,rossion2004revisiting}, whereas captioning or referring expression data sets typically provide less than 10 annotations per entity \cite{devlin:imcaqui,Kazemzadeh2014,mao15}.
% Consequently, a reliable assessment of inter-annotator agreement, speaker preferences, and a deeper linguistic analysis of the observed variation is mostly not possible with available data collections in  L\&V.
% At the same time, these datasets have much potential for research on these topics, as they provide more realistic images of real-world objects and scenes than the idealized drawings used in picture naming norms (see Figure \ref{fig:cake}), as well as a wider coverage of object categories.
% A more systematic understanding of the factors influencing the choice of object names could inform theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal}, as well as the design of models and architectures (e.g.,~Lazaridou et al.~\shortcite{lazaridou-dinu-baroni:2015:ACL-IJCNLP}; Ordonez et al.,~\shortcite{Ordonez:2016}; Zhao et al.,~\shortcite{zhao2017open}).
ManyNames v.1, the version\cs{would remove "the version"} presented in this paper, contains 36 crowd-sourced names for 25K object instances from \vgenome \cite{krishna2016visualgenome}.%
\footnote{Available at \url{https://github.com/amore-upf/manynames}.}
It is inspired in picture naming norms as developed in Psycholinguistics~\cite{snodgrass,rossion2004revisiting}, which is the field that has devoted the most attention to object naming to date.
%\gbt{Is it ``picture naming norms'', or ``naming norms''?}
% Naming norms record naming responses for dozens or hundreds of speakers for the same object.
Picture naming norms are typically small (500-1000 images) and use idealized drawings (Figure \ref{fig:cake}, right; \cs{but see, e.g.,~\cite{brodeur2014bank} for exceptions}); ManyNames is much larger and uses real images of objects in complex visual contexts, which makes it suitable for research in L\&V.
\gbt{should we add footnote citing the naming norms that have real images? (See commented-out tex; \cite{brodeur2014bank} is the ref for the BOSS database.)}
\cs{see the addition in ref to Figure}

@@

% NEW -- I thought we needed to include this discussion, too.
Object names are rarely used in isolation; typically they are embedded in more complex referring expressions, which are themselves embedded in sentences that are part of discourses or dialogues.
However, in the same way that it has proven useful to model referring expressions in visual scenes in an isolated fashion \cite{Kazemzadeh2014,mao15,Yu2016}, we believe there is value in modeling object names on their own.
Questions that need addressing regarding object naming are 1)~how much variation in naming is attested and what factors drive the choice of a name (object category? individual properties of the object? context?); see e.g.\ Rohde et al.~\shortcite{rohde2012communicating} and Graf et al.~\shortcite{graf2016animal}, 2)~how to make L\&V models more human-like with respect to naming, improving the design of L\&V architectures (e.g.,~Lazaridou et al.~\shortcite{lazaridou-dinu-baroni:2015:ACL-IJCNLP}; Ordonez et al.,~\shortcite{Ordonez:2016}; Zhao et al.,~\shortcite{zhao2017open}).
\gbt{I looked at the bst file but I don't know how to make the year appear without parentheses inside the parenthesis.}
% ManyNames can inform both theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal} and on the design of L\&V models and architectures (e.g.,~Lazaridou et al.~\shortcite{lazaridou-dinu-baroni:2015:ACL-IJCNLP}; Ordonez et al.,~\shortcite{Ordonez:2016}; Zhao et al.,~\shortcite{zhao2017open}).
Here, for reasons of scope and space, we provide preliminary results on the amount and type of variation we find in the data.

The trends we identify in the dataset are illustrated in Figure \ref{fig:cake} (left): Our data reveals clear naming preferences (in the example, 53\% of the annotators prefer the name \textit{cake}, corresponding to the so-called basic-level category, see Section~\ref{sec:rel-work}) and also rich variation (the remaining annotators prefer other options like \textit{food, dessert, bread}) that is not restricted to taxonomic relations studied in previous work on naming \cite{Ordonez:2016,graf2016animal}: while \word{food} is in a taxonomic relation to \word{cake} (it is a hypernym), \textit{dessert} highlights a different facet of the object.

>>>>

% GBT revision (I've re-organized the material into paragraphs differently and gone more directly to object names):
A central issue in Language \& Vision (L\&V) is how speakers refer to objects. 
This is most prominent for referring expression generation and interpretation~\cite{Kazemzadeh2014,mao15,Yu2016}, but it also pervades virtually any other L\&V task, such as caption generation or visual dialogue \cite{fangetal:2015,devlin:imcaqui,das2017visual,vries2017guesswhat}.
One of the central components of referring expressions are \textit{object names}; for instance, speakers may name the left object in Figure \ref{fig:cake} \word{cake}, \word{food}, or \word{dessert}, a.o.
This aspect of reference has been understudied in Computational Linguistics and L\&V; as a consequence, it is not clear to what extent current L\&V models capture human naming behavior.
% the factors affecting the choice of a name are far from clear, as is the potential of current L\&V models to successfully model naming data.

@@

% SUBMITTED VERSION:
% Compared to experimental work on perception and language grounding, however, recent data collections in L\&V capture a rather limited amount of inter-speaker variation.
% For instance, picture naming norms used in Psycholinguistics record naming responses for hundreds of speakers for the same object  \cite{snodgrass,rossion2004revisiting}, whereas captioning or referring expression data sets typically provide less than 10 annotations per entity \cite{devlin:imcaqui,Kazemzadeh2014,mao15}.
% Consequently, a reliable assessment of inter-annotator agreement, speaker preferences, and a deeper linguistic analysis of the observed variation is mostly not possible with available data collections in  L\&V.
% At the same time, these datasets have much potential for research on these topics, as they provide more realistic images of real-world objects and scenes than the idealized drawings used in picture naming norms (see Figure \ref{fig:cake}), as well as a wider coverage of object categories.
% A more systematic understanding of the factors influencing the choice of object names could inform theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal}, as well as the design of models and architectures (e.g.,~Lazaridou et al.~\shortcite{lazaridou-dinu-baroni:2015:ACL-IJCNLP}; Ordonez et al.,~\shortcite{Ordonez:2016}; Zhao et al.,~\shortcite{zhao2017open}).
ManyNames v.1, the version\cs{would remove "the version"} presented in this paper, contains 36 crowd-sourced names for 25K object instances from \vgenome \cite{krishna2016visualgenome}.%
\footnote{Available at \url{https://github.com/amore-upf/manynames}.}
It is inspired in picture naming norms as developed in Psycholinguistics~\cite{snodgrass,rossion2004revisiting}, which is the field that has devoted the most attention to object naming to date.
%\gbt{Is it ``picture naming norms'', or ``naming norms''?}
% Naming norms record naming responses for dozens or hundreds of speakers for the same object.
Picture naming norms are typically small (500-1000 images) and use idealized drawings (Figure~\ref{fig:cake}, right; \cs{but see, e.g.,~\cite{brodeur2014bank} for exceptions}); ManyNames is much larger and uses real-world images of objects in complex visual contexts, which makes it suitable for research in L\&V.
%\gbt{should we add footnote citing the naming norms that have real images? (See commented-out tex; \cite{brodeur2014bank} is the ref for the BOSS database.)}
%\cs{see the addition in ref to Figure}

@@

% NEW -- I thought we needed to include this discussion, too.
Object names are rarely used in isolation; typically they are embedded in more complex referring expressions, which are themselves embedded in sentences that are part of discourses or dialogues.
However, in the same way that it has proven useful to model referring expressions in visual scenes in an isolated fashion \cite{Kazemzadeh2014,mao15,Yu2016}, \cs{test models on reasoning abilities over whole scene; we observe instance-based variation, triggered by concrete appearance of object and its context, hence, analogous reasoning is required for naming, too} we believe there is value in modeling object names on their own.
Questions that need addressing regarding object naming are 1)~how much variation in naming is attested and what factors drive the choice of a name (object category? individual properties of the object? context?); see e.g.\ Rohde et al.~\shortcite{rohde2012communicating} and Graf et al.~\shortcite{graf2016animal}, 2)~how to make L\&V models more human-like with respect to naming, improving the design of L\&V architectures (e.g.,~Lazaridou et al.~\shortcite{lazaridou-dinu-baroni:2015:ACL-IJCNLP}; Ordonez et al.,~\shortcite{Ordonez:2016}; Zhao et al.,~\shortcite{zhao2017open}).
\gbt{I looked at the bst file but I don't know how to make the year appear without parentheses inside the parenthesis.}
% ManyNames can inform both theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal} and on the design of L\&V models and architectures (e.g.,~Lazaridou et al.~\shortcite{lazaridou-dinu-baroni:2015:ACL-IJCNLP}; Ordonez et al.,~\shortcite{Ordonez:2016}; Zhao et al.,~\shortcite{zhao2017open}).
Here, for reasons of scope and space, we provide preliminary results on the amount and type of variation we find in the data.

The trends we identify in the dataset are illustrated in Figure \ref{fig:cake} (left): Our data reveals clear naming preferences (in the example, 53\% of the annotators prefer the name \word{cake}, corresponding to the so-called basic-level category, see Section~\ref{sec:rel-work}) and also rich variation (the remaining annotators prefer other options like \word{food, dessert, bread}) that is not restricted to taxonomic relations studied in previous work on naming \cite{Ordonez:2016,graf2016animal}: while \word{food} is in a taxonomic relation to \word{cake} (it is a hypernym), \word{dessert} highlights a different facet of the object.
